\documentclass[12pt,a4paper,sans]{moderncv} 
\moderncvstyle{classic}
\moderncvcolor{blue}
\usepackage{booktabs}
\usepackage[scale=0.85]{geometry} 
\usepackage[none]{hyphenat}%%%%
\firstname{Deepak} 
\familyname{Chethan} 
\title{CSE  B.E. Undergraduate Student,\newline Department of Computer Science Engineering,\newline UVCE, K R Circle, Bangalore.}
\address{\#76/25, Kammasandra}{Electronic city post, Bangalore 560100}
\mobile{+91 7848948784}
\email{deepakchethan@outlook.com}
\homepage{https://deepakchethan.github.io}{https://deepakchethan.github.io}
\begin{document}
\makecvtitle 

\section{Career Objective}
{\space I am a Computer Science Undergraduate with a passion for programming and Software Engineering. I would like to be a part of an organization where I can utilize my programming knowledge to solve challenging problems.}

\section{Education}
	\centering
	\def\arraystretch{1.2}
	\setlength\tabcolsep{6pt}
	\begin{tabular}{|c|c|c|c|c|}
		\hline
		\textbf{Year}& \textbf{Insitute University}                                                                                  & \textbf{Course} & \textbf{Board}                                                            & \textbf{\begin{tabular}[c]{@{}c@{}}Percentage\end{tabular}} \\ \hline
		\begin{tabular}[c]{@{}c@{}}Apr 2015\\ - Present\end{tabular} & \begin{tabular}[c]{@{}c@{}}University Visvesvaraya College of Engineering,\\ KR Circle, Bangalore.\end{tabular} & B.E. CSE      & BU                  & 78.8\%                                                                   \\ \hline
		May 2015                                                       & \begin{tabular}[c]{@{}c@{}}Spurthy Group of Institutions, \\ Anekal\end{tabular}                                & PCMCs           & \begin{tabular}[c]{@{}c@{}}PUE\end{tabular} & 96\%                                                                     \\ \hline
		May 2013                                                       & \begin{tabular}[c]{@{}c@{}}SVREMHS,\\ Chandapura, Bangalore.\end{tabular} & SSLC            & \begin{tabular}[c]{@{}c@{}}KSEEB\end{tabular}           & 96\%                                                                     \\ \hline
	\end{tabular}

\section{Relevant Coursework}
{Data Structures \& Algorithms \textbar \space Computer Networks \textbar \space  Operating Systems  \textbar \space OOP with C++ \textbar \space DBMS}

\section{Research Work}

\cvitem{Title}{Optimizing Multi-path Routing with Guaranteed Fault Tolerance in IOT (In Progress)}
\cvitem{Description}{This research mainly explored the idea of using Hierarchical networking combined with \textit{Least Common Ancestor Algorithm} to improve routing .}

\centering


\section{Technical Skills}

\cvitem{\textbf{Programming}}{\textsc{C/C++},  \textsc{R}, Python, Java\textit{(Basics)}}
\cvitem{\textbf{Web}}{HTML, CSS, Javascript\textit{(Basics)}, NodeJS/ExpressJS}
\cvitem{\textbf{Others}}{Android Development, Shell Scripting}
\cvitem{\textbf{Tools}}{MySQL, Git, ViM, Emacs, Linux.}

\newpage

\section{Projects}

\cventry{Apr$18$--May$18$}{LOCATION BASED SOCIAL NETWORK}{Android App with NodeJS RESTful API}{}{}{A Social networking app where people can post text, images and gifs at various locations and share them with random strangers passing through that path. I used NodeJS with \textit{mongodb} as backend and Android app as client.}

\cventry{Mar $2018$}{RESTAURANT APP | FEST SCHEDULING APP}{}{}{Android Apps}
{Developed as part of an Appathon, Restaurant app is a simple app to automate the ordering and billing process in a hotel and Restaurant based environments. Fest registration app enabled registration of participants with a user friendly interface and provided a way for organizers to keep in touch with the participants via messaging etc.,}

\cventry{Feb $2018$}{ONLINE TREASURE HUNT APP}{Android App}{}{}{This app was developed for event 'Enigma' organized for the fest IMPETUS 18.0. The app facilitated game play in treasure hunt manner with the player information and score details updated online on a Firebase database.}

\cventry{Feb$18$--Mar$18$}{E-COMMERSE WEBSITE}{Web App}{}{}{An E-Commerce site that sells customized sweets was built using NodeJS/ExpressJS as backend paired with mysql database.}

\cventry{Sep$17$--Dec$17$}{PORTABLE DEVELOPMENT ENVIRONMENT}{}{}{Linux}{In this project, I tried to compile an Operating System built on top of the linux kernel directed toward programmers/developers. It supports more than 10 languages out of the box and is designed to be installed and used from a USB device.}


	

\section{Achievements}

\begin{itemize}
	\item[\textbullet] Won second prize in Project Run S1 contest for building and presenting a portable development environment.
	\item[\textbullet] Won second prize in an android hackathon organized by IEEE UVCE as a part of the fest Impetus 18.0.
	\item[\textbullet] Organized the event \textsc{'Enigma'} which is an online treasure hunt for the fest Impetus 18.0.
	\item[\textbullet] I was the Anekal town topper in my PUC board exams.
\end{itemize}
 	 
%Completed the Certificantions, No more new ones!
\section{Certifications}

\cventry{Mar$18$--Curr}{Data Science Specialization}{Johns Hopkins}{Coursera}{}{This Specialization covered the concepts and tools people need throughout the entire data science pipeline.}

\cventry{Aug$17$--Sep$17$}{Machine Learning}{Stanford}{Coursera}{}{This course provided a broad introduction to machine learning, data mining, and statistical pattern recognition.}

\cventry{Jul$17$--Sep$17$}{An Introduction to Programming the Internet of Things (IOT) Specialization}{University of California, Irvine}{Coursera}{}{This Specialization covers embedded systems, the Raspberry Pi Platform, and the Arduino environment for building devices that can control the physical world.}

%----------------------------------------------------------------------------------------

\end{document}